---
title: "exercise"
description: |
  A new article created using the Distill format.
author:
  - name: Nora Jones 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{css, echo = FALSE}
d-article h2 {
  font-family: Rubik;
  font-size: 3em;
  text-align: center;
  border-bottom: 3px solid black;
}
d-article h3 {
  font-size: 1.5em;
  text-align: center;
  font-variant: small-caps;
  font-family: Bitter;
  letter-spacing: .2em;
}
li::marker {
    font-size: 1.2em;
}
```

# In tracking

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

```{r cars, echo=FALSE, fig.width=50}
library(dplyr)
library(echarts4r)
dates <- seq.Date(as.Date("2017-01-01"), as.Date("2018-12-31"), by = "day")
values <- rnorm(length(dates), 20, 6)

year <- data.frame(date = dates, values = values)

year %>% 
  e_charts(date) %>% 
  e_calendar(range = "2018") %>% 
  e_heatmap(values, coord_system = "calendar") %>% 
  e_visual_map(max = 30) %>% 
  e_title("Calendar", "Heatmap")
```

# In my opinion

## 2021

### January

#### 01 week

#### 02 week

#### 03 week

#### 04 week

### February

#### 05 week

#### 06 week

#### 07 week

#### 08 week

#### 09 week

### March

#### 10 week

#### 11 week

#### 12 week

#### 13 week

### April

#### 14 week

#### 15 week

#### 16 week

#### 17 week

### May

#### 18 week

#### 19 week

#### 20 week

#### 21 week

### June

#### 22 week

#### 23 week

#### 24 week

#### 25 week

#### 26 week

### July

#### 27 week

#### 28 week

#### 29 week

#### 30 week

### August

#### 31 week

#### 32 week

#### 33 week

#### 34 week

#### 35 week

### September

#### 36 week

#### 37 week

#### 38 week

#### 39 week

### October

#### 40 week

#### 41 week

#### 42 week

#### 43 week

#### 44 week

### November

#### 45 week

#### 46 week

#### 47 week

#### 48 week

### December

#### 49 week

#### 50 week

#### 51 week

#### 52 week
